PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
Completed intro

These examples show the burgeoning interest of our community for the automatic
learning of social interactions, but also highlight the lack of structure of
these research efforts, as further illustrated by the lack of large, open
datasets of social interactions, suitable for machine-learning applications.

One interesting dataset is the \emph{Multimodal Dyadic Behavior
Dataset} (\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of
3 to 5 minute child-adult interactions. During these interactions, the
experimenter plays with toddlers (1.5 to 2.5 years old) in semi-structured ways.
The dataset includes video streams of the faces and the room, audio, physiological data
(electrodermal activity) as well as manual annotations of certain behaviours
(like gaze to the examiner, laughter, pointing). The lack of calibration and camera positioning
information in the dataset limits the possibilities of automatically extracting and
labelling key interaction features (like facial expressions or joint gaze). Besides,
this dataset focuses on very young children with in adult-driven interactions,
and as such does not include any episodes of naturally-occurring social
interactions between peers.

\todo[inline]{look at other child-child datasets!}
\todo[inline]{mention research on deep-learning to diagnose autism}

@@

\todo[inline]{the dataset is not specific to robotics...PinSoRo is maybe not the
    best name?}

The Plymouth Interacting Social Robots (PInSoRo) Dataset comprises of natural
social interactions arising between children, and recorded with machine learning
applications in mind.

>>>>

These examples show the burgeoning interest of our community for the automatic
learning of social interactions, but also highlight the lack of structured
research efforts, as further illustrated by the limited availability of large
and open datasets of social interactions, suitable for machine-learning
applications.

One such dataset is the \emph{Multimodal Dyadic Behavior Dataset}
(\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of 3 to 5
minute child-adult interactions. During these interactions, the experimenter
plays with toddlers (1.5 to 2.5 years old) in semi-structured ways.  The dataset
includes video streams of the faces and the room, audio, physiological data
(electrodermal activity) as well as manual annotations of specific behaviours
(like gaze to the examiner, laughter, pointing). While this dataset is in
principle relevant, it focuses on very young children during short, adult-driven
interactions. As such, it does not include episodes of naturally-occurring
social interactions between peers, and the diversity of said interactions is
limited. Besides, the lack of intrinsic and extrinsic camera calibration
information in the dataset prevent the automatic extraction and labelling of key
interaction features (like mutual gaze).

Another recent dataset, the \emph{Tower Game Dataset}~\cite{salter2015tower},
focuses specifically on rich dyadic social interactions. The dataset comprises
of 39 adults recorded over a total of 112 annotated sessions of 3 min in
average. The participant are instructed to build together a tower with wooden
blocks. Interestingly, the participants are not allowed to talk in order to
maximise the amount of non-verbal communication. The skeletons and faces of the
participants are recorded, and the dataset is manually annotated with so-called
\emph{Essential Social Interaction Predicates} (ESIPs): rhythmic coupling
(entrainment or attunement), mimicry (behavioral matching), movement
simultaneity, kinematic turn taking patterns, joint attention. The dataset does
not appear to be publicly available on-line.

The PInSoRo dataset shares the aims of the \emph{Tower Game Dataset}, with
however a stronger focus on natural, real-world behaviours: as presented in the
following sections, we record much longer interactions (up to 40 minutes) of
free-play interaction, fostering a wider range of socio-cognitive behaviours.

@@

The Plymouth Interacting Social Robots (PInSoRo) Dataset comprises of natural
social interactions arising between children, and recorded with machine learning
and social robotics applications in mind.
